Drivers of sex differences in consumption

### 2017-06-05 sex-difference/sex-difference.Rmd
sex

```{r drug_by_sex_plot}
ubs %>%
  ggplot(aes(x=male, y=female, label=antibiotic)) +
  geom_text() +
  geom_point() +
  geom_abline() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal() +
  coord_fixed()
```

>>>>

```{r drug_by_sex_plot}
ubs %>%
  mutate(highlight=antibiotic %in% c('azithromycin', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'fosfomycin', 'nitrofurantoin')) %>%
  ggplot(aes(x=male, y=female, label=antibiotic, color=highlight)) +
  geom_text() +
  geom_point() +
  geom_abline() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal() +
  coord_fixed()
```
